Unifying the communicable disease spreading paradigm with Gompertzian growth

### 2022-12-19 arxiv/main.tex
moved paragraph about macroscopic assumptions

 Perhaps a more likely scenario from which a Gompertz curve would emerge is the selective infection of central nodes in the transmission network resulting in an immediate decrease in relative growth. 
 Herrmann and Schwartz (2020) \cite{herrmann2020covid} studied a networked SIR model on a variety of networks, but did not elaborate on a possible fit to a Gompertz curve. Estrada and Bartesaghi (2022) \cite{estrada2022networked} found that the Gompertz curve can emerge in later stages of an SIS (Susceptible-Infected-Susceptible) model, but not in the beginning of an SIR-like model.
 Although it may be possible to realize Gompertzian growth from a special network, firm theoretical work has yet to be done to show this connection. 
 We will touch upon how the Gompertz curve emerges from one such network below, under some caveats.

@@

More generally, the SIR model family considers averaged macroscopic behavior of an ensemble of microscopic units justified through mean-field theory \cite{smilkov2014beyond} which does not consider network effects explicitly. Rather, all entities are connected and communicating through long-range interactions as shown by Mombach et al. (2002) \cite{mombach2002mean}.
However, even with such strong assumptions, it is odd that observed mortality never exhibits a stage of near-exponential growth as this macroscopic SIRD model predicts, but rather a constant negative slope in the double-log-domain. We are thus prompted to look for another model which can explain the observed mortality patterns.

@@

Finally, we are positioned to arrive at a closed-form expression for a finite number of interaction terms in this modified logistic model, which represents the infection term in the SIR model. Working with a single unitless growth variable and omitting the multivariate network without loss of generality, we start with

>>>>

 Perhaps a more likely scenario from which a Gompertz curve would emerge is the selective infection of central nodes in the transmission network resulting in an immediate decrease in relative growth. 
 Herrmann and Schwartz (2020) \cite{herrmann2020covid} studied a networked SIR model on a variety of networks, but did not elaborate on a possible fit to a Gompertz curve. Estrada and Bartesaghi (2022) \cite{estrada2022networked} found that the Gompertz curve can emerge in later stages of an SIS (Susceptible-Infected-Susceptible) model, but not in the beginning of an SIR-like model.
 Although it may be possible to realize Gompertzian growth from a special network, firm theoretical work has yet to be done to establish this connection. 
 We will touch upon how the Gompertz curve emerges from one such network below, under some caveats.

 In general, the SIR models and their extensions which do not consider network interactions explicitly consider rather averaged macroscopic behavior of an ensemble of microscopic units justified through mean-field theory \cite{smilkov2014beyond}. In such models, all entities are connected and communicating through long-range interactions as shown by Mombach et al. (2002) \cite{mombach2002mean}.
However, even with such strong assumptions, it is odd that observed mortality never exhibits a stage of near-exponential growth as this macroscopic SIR model family predicts, but rather a constant negative slope in the double-log-domain, which we will now show.

@@

In summary, we see that the SIR model family both lacks the observed immediate decrease in relative growth rate, and makes strong assumptions about the disease spreading network structure that imply non-local interactions. We are thus prompted to look for another model which can explain the observed mortality patterns.

@@

\subsection*{A closed-form expression for a unified model}
Finally, we are positioned to arrive at a closed-form expression for a finite number of interaction terms in this modified logistic model, which represents the infection term in the SIR model. Working with a single unitless growth variable and omitting the multivariate network without loss of generality, we start with
